### 2013-10-20 msthesis.tex
minor mod
modified title page format to conform with original

%% Replace the title, name, advisor name, graduation date and dedication below with
%% your own. Graduation months must be January, May or September.
\newcommand{\thesistitle}{A Lanczos Procedure for Approximating Eigenvalues of Large Stochastic Matrices}
\newcommand{\thesisauthor}{William J. DeMeo}
\newcommand{\thesisadvisor}{Professor Jonathan Goodman}
\newcommand{\graddate}{Jan 1999}

@@

%%%%%% Title page %%%%%%%%%%%
%% Sets page numbering to "roman style" i, ii, iii, iv, etc:
\pagenumbering{roman}
%
%% No numbering in the title page:
\thispagestyle{empty}
%
\begin{center}
  {\large\textbf{\thesistitle}}
  \vspace{.7in}

  by
  \vspace{.7in}

  \thesisauthor
  \vfill

\begin{doublespace}
  A dissertation submitted in partial fulfillment\\
  of the requirements for the degree of\\
  Master of Science\\
  Department of Mathematics\\
  New York University\\
  \graddate
\end{doublespace}
\end{center}
\vfill

>>>>

%% Replace the title, name, advisor name, graduation date and dedication below with
%% your own. Graduation months must be January, May or September.
\newcommand{\thesistitle}{A Lanczos Procedure for Approximating Eigenvalues of Large Stochastic Matrices}
\newcommand{\thesisauthor}{William J. DeMeo}
\newcommand{\thesisadvisor}{Professor Jonathan Goodman}
\newcommand{\graddate}{January 1999}

@@

%%%%%% Title page %%%%%%%%%%%
%% Sets page numbering to "roman style" i, ii, iii, iv, etc:
\pagenumbering{roman}
%
%% No numbering in the title page:
\thispagestyle{empty}
%
\begin{center}
  {\large\textbf{\thesistitle}}

  \vspace{5mm}

  by

  \vspace{5mm}

  \thesisauthor

  \vfill

%% \begin{doublespace}
  A dissertation submitted in partial satisfaction of the\\[-4pt]
  requirements for the degree of\\[-4pt]
  Master of Science\\[6pt]
  in\\[6pt]
  Mathematics\\[6pt]
  in the\\[6pt]
  GRADUATE DIVISION\\[-4pt]
  of the \\[-4pt]
  NEW YORK UNIVERSITY\\
%% \end{doublespace}
\end{center}
Committee in charge:\\
\phantom{XXX} Professor Jonathan Goodman, Chair\\[-4pt]
\phantom{XXX} Professor Leslie Greengard
\begin{center}
  \graddate
\end{center}
\vfill
